### 2015-02-06 paper_20_sdo.tex
adding a reference

    Software engineering has struggled to determine the correct projects to complete \cite{DeMarco2009}.
    Software projects are typically behind schedule and over budget. Organizations need a better
    technique to understand the past performance so they can better predict the future performance.

>>>>

    Software engineering has struggled to determine the correct projects to complete \cite{DeMarco2009}.
    Software projects are commonly behind schedule and over budget. Organizations need a better
    technique to understand the past performance so they can better predict the future performance \cite{Lehtinen2014}.
